Descriptive stuff

### 2023-05-09 notebook/descriptive.qmd
Finish "Where are NGOs based" section

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(sf)
library(scales)
library(gt)
library(here)

@@

```{r tb-who-responded-others}
survey_orgs %>%
  filter(!is.na(Q2.3_TEXT)) %>%
  mutate(`Position in organization` = str_to_title(Q2.3_TEXT)) %>%
  group_by(`Position in organization`) %>%
  summarise(Count = n()) %>%
  mutate(Proportion = Count / sum(Count)) %>%
  arrange(desc(Count)) %>% 
  gt() %>% 
  fmt_percent(columns = Proportion, decimals = 1) %>% 
  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE) %>% 
  opt_table_font(font = "Fira Sans")
```

@@

```{r process-map}
df_hq_countries <- survey_orgs %>% 
  group_by(Q2.2_iso3) %>% 
  summarize(num_ngos = n()) %>% 
  mutate(num_ngos_ceiling = ifelse(num_ngos >= 30, 30, num_ngos),
         ngo_presence = ifelse(num_ngos >= 1, "At least one NGO respondent", NA))

map_hq <- world_map %>% 
  left_join(df_hq_countries, by = join_by(ISO_A3 == Q2.2_iso3))
```

```{r plot-map-respondents-gradient}
ggplot() +
  geom_sf(data = map_hq, aes(fill = num_ngos_ceiling),
          linewidth = 0.1, color = "grey30") +
  scale_fill_binned(low = clrs$Peach[1], high = clrs$Peach[7], na.value = "grey95",
                    labels = c(1, 10, 20, "30+"), breaks = c(1, 10, 20, 30),
                    name = "Number of NGOs: ",
                    guide = guide_colorsteps(barwidth = 7, barheight = 0.4,
                                             title.vjust = 1)) +
  coord_sf(crs = "+proj=robin") +
  theme_ingo_map()
```

>>>>

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(sf)
library(countrycode)
library(scales)
library(gt)
library(here)

@@

```{r tab-who-responded-others}
survey_orgs %>%
  filter(!is.na(Q2.3_TEXT)) %>%
  mutate(`Position in organization` = str_to_title(Q2.3_TEXT)) %>%
  group_by(`Position in organization`) %>%
  summarise(Count = n()) %>%
  mutate(Proportion = Count / sum(Count)) %>%
  arrange(desc(Count)) %>% 
  gt() %>% 
  fmt_percent(columns = Proportion, decimals = 1) %>% 
  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE) %>% 
  opt_table_font(font = "Fira Sans")
```

@@

## How are these NGOs distributed by HQ?

```{r tab-hq-countries}
df_hq_countries <- survey_orgs %>% 
  group_by(Q2.2_iso3) %>% 
  summarize(num_ngos = n()) %>% 
  mutate(num_ngos_ceiling = ifelse(num_ngos >= 30, 30, num_ngos),
         ngo_presence = ifelse(num_ngos >= 1, "At least one NGO respondent", NA),
         prop = num_ngos / sum(num_ngos)) %>% 
  mutate(country_name = countrycode(Q2.2_iso3, "iso3c", "country.name")) %>%
  arrange(desc(num_ngos))

df_hq_countries %>% 
  select(country_name, Q2.2_iso3, num_ngos, prop) %>%
  gt() %>% 
  cols_label(
    country_name = "Country name",
    Q2.2_iso3 = "ISO3",
    num_ngos = "NGOs",
    prop = "Proportion"
  ) %>% 
  fmt_percent(columns = prop, decimals = 1) %>% 
  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE) %>% 
  opt_table_font(font = "Fira Sans")
```

## Number of unique HQ countries

```{r}
#| code-fold: show
df_hq_countries %>% 
  summarize(total = sum(num_ngos >= 1))
```

## Regional distribution of HQ countries

```{r tab-hq-regions}
df_hq_regions <- df_hq_countries %>%
  mutate(region = countrycode(Q2.2_iso3, "iso3c", "continent"),
         region = ifelse(Q2.2_iso3 == "TWN", "Asia", region)) %>%
  mutate(region = recode(region, Oceania = "Asia &\nOceania", Asia = "Asia &\nOceania")) %>%
  group_by(region) %>%
  summarise(num = sum(num_ngos)) %>% ungroup() %>%
  mutate(prop = num / sum(num)) %>%
  arrange(desc(num)) %>%
  mutate(region = fct_rev(fct_inorder(region)))

df_hq_regions %>% 
  gt() %>% 
  cols_label(
    region = "Region",
    num = "NGOs",
    prop = "Proportion"
  ) %>% 
  fmt_percent(columns = prop, decimals = 1) %>% 
  cols_align(align = "left", columns = region) %>% 
  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, 
                  use_pagination = FALSE, use_pagination_info = FALSE) %>% 
  opt_table_font(font = "Fira Sans")
```

```{r plot-hq-regions, fig.width=6, fig.height=3}
ggplot(df_hq_regions, aes(x = num, y = region)) +
  geom_pointrange(aes(xmin = 0, xmax = num)) +
  scale_x_continuous(sec.axis = sec_axis(~ . / sum(df_hq_regions$num),
                                         labels = label_percent())) +
  labs(x = "Respondents based in region", y = NULL,
       title = "Region of headquarters",
       subtitle = "Q2.2: Where is your organization's headquarters? (summarized by region)") +
  theme_ingo() + 
  theme(panel.grid.major.y = element_blank())
```

## Responses per country (30 NGO ceiling)

```{r plot-map-respondents-gradient}
map_hq <- world_map %>% 
  left_join(df_hq_countries, by = join_by(ISO_A3 == Q2.2_iso3))

ggplot() +
  geom_sf(data = map_hq, aes(fill = num_ngos_ceiling),
          linewidth = 0.1, color = "grey30") +
  scale_fill_binned(low = clrs$Peach[1], high = clrs$Peach[7], na.value = "grey95",
                    labels = c(1, 10, 20, "30+"), breaks = c(1, 10, 20, 30),
                    name = "Number of NGOs: ",
                    guide = guide_colorsteps(barwidth = 7, barheight = 0.4,
                                             title.vjust = 1)) +
  coord_sf(crs = "+proj=robin") +
  theme_ingo_map()
```

## Countries with at least one response
